\begin{frame}{DNS exercise (1)}
    \begin{itemize}
    \item ``www.cs.virginia.edu is 128.148.67.11 \myemph{for next 86400 seconds}''
    \item (given record above)
    if sysadmin changes IP address DNS server returns for www.cs.virginia.edu,
    then what will happen to machines accessing website?
        \begin{itemize}
        \item A. they'll start using the new address after 86400 seconds, and use the old one before then.
        \item B. different machines will use the new address at different times, but no longer than 86400 seconds from when it changes
        \item C. machines will start using the new address almost immediately, but after some small delay after it is changed
        \item D. machines may keep using the old address until they are rebooted
        \item E. something else?
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{DNS exercise (2)}
    \begin{itemize}
    \item if sysadmin wants to change the IP address of www.cs.virginia.edu,
            how do they do this without downtime?
    \vspace{.5cm}
    \item they can change the IP address the server returns and/or the time-to-live?
    \item what should they change and when to smoothly transition to a new address?
    \end{itemize}
\end{frame}

\begin{frame}{DNS exercise (3)}
    \begin{itemize}
    \item suppose initially
        \begin{itemize}
        \item *.foo.com DNS server (`nameserver') = 10.2.3.4, valid 200 s
        \item www.foo.com = 10.1.2.3, valid 100 s
        \end{itemize}
    \item if at time 0 seconds, changed to:
        \begin{itemize}
        \item *.foo.com DNS server = 10.3.4.5, valid 100 s
        \item www.foo.com DNS server = 10.3.5.1, valid 400 s
        \end{itemize}
    \item ex 0: when will new DNS server/www.foo.com start being used?
    \item ex 1: when can we shut down old DNS server?
    \item ex 2: when can we shut down old www.foo.com?
    \end{itemize}
\end{frame}
