\begin{frame}{DNSKEY / DS}
\begin{itemize}
    \item DNSKEY records hold public keys
        \begin{itemize}
        \item gives zone key is intended for
        \item doesn't tell you the key is actually good
        \end{itemize}
    \item DS records delegate from key to another
        \begin{itemize}
        \item each DNSKEY needs corresponding DS record
        \item DS record contains hash of DNSKEY + related info
        \end{itemize}
    \item DS records signed using RRSIG records
        \begin{itemize}
        \item combination of DS + DNSKEY tells you key is good
        \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{multiple DNSKEYs}
    \begin{itemize}
    \item can/usually do have multiple keys per zone
    \item typically ``Key-Signing Key'' (KSK) + ``Zone-Signing Key'' (ZSK)
    \item goal: if ZSK is compromised, replace it
    \item keep KSK protected much more heavily than ZS
    \end{itemize}
\end{frame}

\begin{frame}[fragile]{DNSKEY/DS signing}
\begin{Verbatim}[fontsize=\fontsize{9}{10}]
;; records maintained by com. server:
cloudflare.com. 86400 IN DS     2371 13 2 329968....F6D6 3826F2B9
cloudflare.com. 86400 IN RRSIG  DS 13 2 86400 20241030011127 20241023000127 29942 com. wo...k80C Nfk...mZsYw==
cloudflare.com. 3600  IN DNSKEY 257 3 13 mdss...kHAeF+ KkxL...KGQ==

;; records maintained by cloudflare.com. servers:
cloudflare.com. 3600  IN DNSKEY 256 3 13 oJMRES...5ar0IRd8 KqXXF...hSA==
cloudflare.com. 3600  IN RRSIG DNSKEY ...
\end{Verbatim}
\begin{itemize}
\item DS record signed by com. keyid 29942
\item `flags' of 257 = key-signing key, 256 = zone-signing key
    \begin{itemize}
    \item not the key tag, that's derived from key itself
    \end{itemize}
\item RRSIG verifies that zone-signing key is endorsed from key-signing key
\end{itemize}
\end{frame}
